Bridging [TBD]

### 2014-03-18 paper/draft.tex
Relecture NDSS

Furthermore, DeHype \cite{wu2013TamHosHypMosDepExe} presented an dissected version of KVM hypervisor, trying to reduce the TCB of this popular hypervisor. The approach consisted in demoting a great part of the hypervisor codebase to a user-level execution. DeHype satisfies all vertical design principles listed before (DS1,DS2,DS3), reinterpreting the microkernel approach of  demoting the greatest part of code to userspace. DeHype increases a lot the robustness of a cloud platform leveraging KVM, limiting for example the possibility of attack in multi-tenancy platform, but it does not address horizontal design principles about a multi-provider service.

>>>>

% Integration NDSS Taming
Furthermore, DeHype \cite{wu2013TamHosHypMosDepExe} presented a dissected version of KVM hypervisor, trying to reduce the TCB of this popular hypervisor. The approach consisted in demoting a great part of the hypervisor codebase to a user-level execution. DeHype satisfies all vertical design principles listed before (DS1,DS2,DS3), reinterpreting the microkernel approach of demoting the greatest part of code to userspace. DeHype increases a lot the robustness of a cloud platform leveraging KVM, limiting for example the possibility of attack in multi-tenancy platform, but it does not address horizontal design principles about a multi-provider service.
